---
title: "Inference Practice Notebook"
output: html_notebook
---
For the first practice here we will be using 

1.  Load the [](Data/cleanTeslaBattery.csv) and run a quick summary to view your data.
```{r}

```

2. Use what you have already learned to plot the relationship between ```WattHoursPerKM``` and ```MileageKM```.
```{r}

```

3.  We will perform a linear regression using the ```lm()``` function.  The syntax requires a function describing the form ```(y ~ x)``` as you have seen in other cases, and the name of the data.

```{r}

```

4.  Go back and assign a name to the previous model and rerun it so that we can use the name in other analyses.  

5.  You will notice that the model doesn't produce all of the values we might want.  You can now apply the ```summary()``` command to your model to get statistics on the regression model.
```{r}

```


6.  R allows easy accessibility to other things you may want for inspecting the quality of your regression fit.  For example, run the command ```hist(residuals(mod))``` in the box below.  What would you expect it to produce?
```{r}

```

7. R also makes transformations of data very simple.  Run the code below, which model gives the best fit?

```{r}
# a log transform
summary(lm(WattHoursPerKM ~ log(MileageKM), data = cleanTeslaBattery))

# a sqrt transform
summary(lm(sqrt(WattHoursPerKM) ~ MileageKM, data = cleanTeslaBattery))
```

8. Now we will try a *t*-test.  Load the Kings county birth data [](Data/KingCounty2001.csv) and check a quick summary to make sure it loaded as you would expect.
```{r}

```

9.  Next we are going to run a test to determine if the smoking status of the mother has a significant effect (```smoker```) on weight gain (```wgain```) using the ```t.test()``` command with a relational input describing the two variables you want to compare and the name of the data.
```{r}

```
What useful information is provided in the output that your introductory students might want?

10.  The default is to a two-sided test, but this can be easily controlled by using the option ```alternative = "less"``` or ```alternative = "greater"``` options.  Modify your previous command for a one-sided greater than alternative.

```{r}

```

What do you notice about the confidence interval given?  Students often forget this so it is helpful to remind them.
