---
title: "R Packages for Learning"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment="") 
```

## Base R vs. Packages for Learning  

In 2001, a sample of 2500 births from King County, Washington contained information on both the mother and the infant at birth. Load in the data `KingCounty2011.csv`
```{r}
king<-read.csv()
```

Suppose we want to compare the birth weight (`bwt`) of a baby between mothers who smoke (Y) versus do not smoke (N) (`smoker`).  

In base R, here is what the code would look like:

```{r}
mean(king$bwt[king$smoker=="Y"]) #smoke
mean(king$bwt[king$smoker=="N"]) #do not smoke
```

How would we calculate the standard deviation as well?

```{r}

```

## Package mosaic  

The `mosaic` package was developed by Randall Pruim, Danny Kaplan, and Nicholas Horton.  The goal of [Project mosiac](http://mosaic-web.org/) is to support the learning of R in colleges and universities.  Let's try our previous problem using functions in `mosaic`.  

First, install the package if you haven't done so already.  

Now, before we load the package, let's take a peak at the `mean()` function in base R.  What error results?

```{r}
mean(king$bwt~king$smoker)
```


Now load the `mosaic` pacakge and note the message provided when loaded.

```{r}

```


We can now run our `mean()` function (overwritten by `mosaic`)
```{r}
mean(bwt~smoker, data=king)
```

Many of the summary statistic functions of base R will now work in function form.  `mosaic` also adds new functions, such as `favstats` 

```{r}
favstats(bwt~smoker, data=king)
```

In addition, it allows for some simple graphics that allow faceting:  

```{r}
histogram(~bwt|smoker, data=king)
```

and easy bargraphs without the need to create a count table:
```{r}
bargraph(~smoker, data=king)
```

and overlay summary values: 
```{r}
histogram(~bwt, v=2500, data = king)
```


## Package ggformula  
You can easily "pipe" using the ` %>% ` symbol to overlay two graphs and you can use many of the `ggplot2` arguments within the `ggformula` functions.  For example:
```{r}
library(ggformula)
gf_boxplot(bwt~smoker, data=king) %>% 
  gf_violin(bwt~smoker, data=king, fill=~smoker, alpha=0.3)
```

Try out a few other plots using the King County birthweight data and `ggformula`.  



# Packages for Learning R - Swirl

To get started, you just have to load the library (after you install it of course).

```{r}
library(swirl)
```




